GlobalSearchRegression.jl \\ \vspace{5mm} REPORT

### 2019-07-26 src/Output/decorations/latex/tpl.tex
Intelligent text

\begin{table}[!h]
  \centering
  \caption{K-fold cross-validation Results}
    \begin{tabular}{l c c}
    \hline
    \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}}    \\
                    & {{kfolds}}-fold         & {{kfolds}}-fold \\
    Variables       & Mean                    & Median          \\
    \hline
    \hline
{{ median }}
--
{{ average }}
    {{#kfoldvars}}
      {{ varname }} & {{ meancoef }}{{stars}} & {{ mediancoef }}{{stars}} \\
                    & {{ meanstd }}           & {{ medianstd }}           \\
    {{/kfoldvars}}
    \hline

    Error out-sample &     &   \\
                     &     &   \\
    \hline
    \hline
    \multicolumn{3}{c}{\textit{Standard errors in parentheses}} \\
    \multicolumn{3}{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}
{{/crossvalidation}}

>>>>

\begin{table}[!h]
  \centering
  \caption{K-fold cross-validation Results}
    \begin{tabular}{l c c}
    \hline
    \multicolumn{3}{c}{K-fold scheme:\textbf{Insert scheme}}                             \\
               &                  \multicolumn{2}{c}{ {{kfolds}}-fold }                  \\
    Variables  & Mean                             & Median                               \\
    \hline
    \hline
    {{#kfoldvars}}
    {{name}}   & {{#mean}}{{b}}{{stars}}{{/mean}} & {{#median}}{{b}}{{stars}}{{/median}} \\
               & {{#mean}}{{bstd}}{{/mean}}       & {{#median}}{{bstd}}{{/median}}       \\
    {{/kfoldvars}}
    \hline

    Error out-sample &  {{#outsample}}{{mean}}{{/outsample}}   & {{#outsample}}{{median}}{{/outsample}} \\
    \hline
    \hline
    \multicolumn{3}{c}{\textit{Standard errors in parentheses}} \\
    \multicolumn{3}{c}{*** p < 0.01, ** p < 0.05, * p < 0.1} \\
    \hline
    \end{tabular}
  \label{tab:addlabel}
\end{table}
{{/crossvalidation}}
